\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-20 paper.qmd
Added long edges figures

<!--add vis showing removing the hexagons using first quantile, and observing neighbors-->
<!--Using first quantile as the benchmark value-->
```{r}
hex_grid_with_low_counts <- full_join(hex_grid2, 
    df_bin_centroids_scurve, 
    by = c("hex_poly_id" = "hexID")) |>
  filter(!is.na(std_counts)) |>
  mutate(type = if_else(std_counts <= benchmark1, "low", "high")) |>
  filter(type == "low")

@@

@@

```{r}
#| echo: false
#| label: fig-lwd-scurve
#| fig-pos: H
#| fig-cap: "(a) Identification of low-density hexagons using a benchmark value of $0.158$, and (c) Identification of low-density hexagons considering neighboring bins."
#| fig-width: 9
#| fig-height: 6

@@

<!--add distribution of distance along with the default benchmark-->

```{r}
## Triangulate bin centroids
tr1_object_scurve <- tri_bin_centroids(
  df_bin_centroids_scurve, x = "c_x", y = "c_y")
tr_from_to_df_scurve <- gen_edges(
  tri_object = tr1_object_scurve)

@@

<!--show the trimesh with colored long edges with different benchmark values-->

>>>>

<!--Using first quantile as the benchmark value-->
```{r}
hex_grid_with_low_counts <- full_join(hex_grid2, 
    df_bin_centroids_scurve, 
    by = c("hex_poly_id" = "hexID")) |>
  filter(!is.na(std_counts)) |>
  mutate(type = if_else(std_counts <= benchmark1, "low", "high")) |>
  filter(type == "low")

@@

df_bin_centroids_scurve_keep  <- df_bin_centroids_scurve |>
  filter(!(hexID %in%remove_id))

@@

```{r}
#| echo: false
#| label: fig-lwd-scurve
#| fig-pos: H
#| fig-cap: "(a) Identification of low-density hexagons using a benchmark value of $0.242$, and (c) Identification of low-density hexagons considering neighboring bins."
#| fig-width: 9
#| fig-height: 6

@@

<!--distribution of distance along with the default benchmark-->
```{r}
## Triangulate bin centroids
tr1_object_scurve <- tri_bin_centroids(
  df_bin_centroids_scurve_keep, x = "c_x", y = "c_y")
tr_from_to_df_scurve <- gen_edges(
  tri_object = tr1_object_scurve)

@@

<!--trimesh with different benchmark values-->

```{r}
## With calculated default: 0.201
trimesh_lg_scurve1 <- vis_rmlg_mesh(
  distance_edges = distance_scurve, 
  benchmark_value = benchmark_scurve, 
  tr_coord_df = tr_from_to_df_scurve, 
  distance_col = "distance") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a", sc_ltr_pos)

trimesh_lg_scurve2 <- vis_rmlg_mesh(
  distance_edges = distance_scurve, 
  benchmark_value = 0.35, 
  tr_coord_df = tr_from_to_df_scurve, 
  distance_col = "distance") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b", sc_ltr_pos)

trimesh_lg_scurve3 <- vis_rmlg_mesh(
  distance_edges = distance_scurve, 
  benchmark_value = 1.1, 
  tr_coord_df = tr_from_to_df_scurve, 
  distance_col = "distance") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c", sc_ltr_pos) 
```

```{r}
#| echo: false
#| label: fig-lg-scurve
#| fig-pos: H
#| fig-cap: "$2\\text{-}D$ model generated for different benchamrk values to remove long edges: (a) benchmark = $0.201$ (default), (b) benchmark = $0.35$, and (c) benchmark = $1.1$. What is the effective benchmark value to remove long edges?"
#| fig-width: 6
#| fig-height: 3

trimesh_lg_scurve1 + trimesh_lg_scurve2 + trimesh_lg_scurve3 +
  plot_layout(guides='collect', ncol = 3) &
  theme(legend.position='none', plot.tag = element_text(size = 8))
```

### 2024-05-20 paper.tex
Added long edges figures

\caption{\label{fig-lwd-scurve}(a) Identification of low-density
hexagons using a benchmark value of \(0.158\), and (c) Identification of
low-density hexagons considering neighboring bins.}

@@

>>>>

\caption{\label{fig-lwd-scurve}(a) Identification of low-density
hexagons using a benchmark value of \(0.242\), and (c) Identification of
low-density hexagons considering neighboring bins.}

@@

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-lg-scurve-1.pdf}

\caption{\label{fig-lg-scurve}\(2\text{-}D\) model generated for
different benchamrk values to remove long edges: (a) benchmark =
\(0.201\) (default), (b) benchmark = \(0.35\), and (c) benchmark =
\(1.1\). What is the effective benchmark value to remove long edges?}
